---
title: "KNN_Ocupation"
format: html
editor: visual
author: "Ha Trang Nguyen"
reviewer: "Minh Le Ngoc Nguyen"
Date: "20/09/2022"
---

## Model purpose

This model objective is to analyze the data set about characteristics of the occupancy and define whether the occupancy is available or not using KNN.

## Setting up/ Installing packages

```{r}
library(tidyverse)
library("class")
library("caret")
library(readr)
```

## Reading data

```{r}
link <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s2y2122-LilSagi/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(link)
View(rawDF)
```

## Data understanding

```{r}
str(rawDF)
```

## Data preparation

```{r}
#Excluding the first column because the value is unique and can not be used in the model
cleandf <- rawDF[-1]
head(cleandf)
```

```{r}
countOccu <- table(cleandf$Occupancy)
propOccu <- round(prop.table(countOccu) * 100 , digits = 1)

countOccu
propOccu
```

```{r}
cleandf$Occupancy <- factor(cleandf$Occupancy)

```

```{r}
summary(cleandf[1:5])
```

## Normalizing variables (building function of normalization)

```{r}
normalize <- function(x) { # Function takes in a vector
  return ((x - min(x)) / (max(x) - min(x))) # distance of item value - minimum vector value divided by the range of all vector values
}

testSet1 <- c(1:5)
testSet2 <- c(1:5) * 10

cat("testSet1:", testSet1, "\n")
cat("testSet2:", testSet2, "\n")
cat("Normalized testSet1:", normalize(testSet1), "\n")
cat("Normalized testSet2:", normalize(testSet2))
```

## Normalizing data variables

```{r}
?dim
nCols <- dim(cleandf)[2] -1
nCols
cleandf_n <- sapply(1:nCols,
                    function(x) {
  normalize(cleandf[,x])
}) %>% as.data.frame()

cleandf_n

summary(cleandf_n)
```

## Splitting data into training and test sets

```{r}
trainDF_features <- cleandf[1:6987,  ]  
trainDF_features
testDF_features <- cleandf[6988:8143,  ]
testDF_features
```

```{r}
train_df_labels <- cleandf[1:6987,  6]
train_df_labels
test_df_labels <- cleandf[6988:8143,  6]
test_df_labels
```

# Modeling and evaluating

```{r}
cleandf_test_pred <- knn(train = as.matrix(trainDF_features), test = as.matrix(testDF_features), cl = as.matrix(train_df_labels), k = 21)
head(cleandf_test_pred)
is.factor(cleandf_test_pred)
```

## Making diffusion table

```{r}
test_df_labels$Occupancy <- factor(test_df_labels$Occupancy)
is.factor(test_df_labels$Occupancy)
confusionMatrix(cleandf_test_pred, test_df_labels[[1]], positive = NULL, 
                dnn = c("Prediction", "True"))
```

With k=21, it shows that the accuracy reaches 99.39% which is the highest result when running this model. There are some articles mentioning that the way to select the k-value is to set k= sqrt(n). In this case, it would mean that k= sqrt(8143) = 90. However, the accuracy I got when selecting k= 90 is 95.5%, which is lower than the one I got with k=21.

Although the teacher stated that choosing the k-value is mostly based on feelings, I still wonder if there is a proper way to determine which value should be selected as k in KNN. If the reviewer has any ideas about this topic, you may add suggestion to improve the model.
